Poster Data Analysis

### 2018-09-09 notebooks/poster_analysis.Rmd
changed output of stats table
added chisq tests for all acquired and all mutations

# Functions

@@

## COnfidence intervals
get_binCI <- function(x, n) as.numeric(setNames(binom.test(x,n)$conf.int*100,
                                                c("lwr", "upr")))
```

@@

create_corr_matrix <- function(df) {
  df <- df %>%
    as.matrix %>%
    cor %>%
    as.data.frame %>%
    rownames_to_column(var = "var1") %>%
    gather(var2, value, -var1) %>%
    mutate(var1 = gsub("(.*?)_R$", "\\1", var1),
           var2 = gsub("(.*?)_R$", "\\1", var2))
  return(df)
}

@@

## Significance test for the percent presence of qnrB19 and qnrS1 between animal species
```{r message=FALSE, warning=FALSE}
specific_qnr <- qnr_data %>%
  filter(key %in% c("qnrB19", "qnrS1")) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

do_chisq_test <- function(df) {
  df <- df %>%
    slice(expand.grid(1:length(unique(species)), 1:length(unique(species))) %>% rev %>% 
          filter(Var2 < Var1) %>% t) %>%
    mutate(test = rep(1:(n()/2), each = 2)) %>%
    group_by(test) %>%
    do(data_frame(gene = .$key,
                  test = first(.$test),
                  species1 = first(.$species),
                  species2 = last(.$species),
                  data = list(matrix(c(.$Absent,
                                       .$Present),
                                     ncol = 2)))) %>%
    mutate(chi_test = map(data, chisq.test, correct = FALSE)) %>%
    mutate(p.value = map_dbl(chi_test, "p.value"),
           dupl = duplicated(test)) %>%
    filter(dupl == FALSE) %>%
    select(gene, species1, species2, p.value) %>%
    filter(p.value < 0.05)
  return(df)
}

p_values <- lapply(specific_qnr, function(x) do_chisq_test(x)) %>%
  bind_rows(.id = "gene")

p_values
```

>>>>

# Functions
This chunk lists the functions used in this notebook.
```{r}
# Functions

@@

## COnfidence intervals
get_binCI <- function(x, n) as.numeric(setNames(binom.test(x,n)$conf.int*100,
                                                c("lwr", "upr")))

# Creates a correlation matrix from 1/0 data from MIC values
create_corr_matrix <- function(df) {
  df <- df %>%
    as.matrix %>%
    cor %>%
    as.data.frame %>%
    rownames_to_column(var = "var1") %>%
    gather(var2, value, -var1) %>%
    mutate(var1 = gsub("(.*?)_R$", "\\1", var1),
           var2 = gsub("(.*?)_R$", "\\1", var2))
  return(df)
}

# Creates a data frame with p-values for comparing presence of specific genes between animal species
do_chisq_test <- function(df) {
  df <- df %>%
    slice(expand.grid(1:length(unique(species)), 1:length(unique(species))) %>% rev %>% 
          filter(Var2 < Var1) %>% t) %>%
    mutate(test = rep(1:(n()/2), each = 2)) %>%
    group_by(test) %>%
    do(data_frame(gene = .$key,
                  test = first(.$test),
                  species1 = first(.$species),
                  species2 = last(.$species),
                  data = list(matrix(c(.$Absent,
                                       .$Present),
                                     ncol = 2)))) %>%
    mutate(chi_test = map(data, chisq.test, correct = FALSE)) %>%
    mutate(p.value = map_dbl(chi_test, "p.value"),
           dupl = duplicated(test)) %>%
    filter(dupl == FALSE) %>%
    select(gene, species1, species2, p.value) %>%
    filter(p.value < 0.05)
  return(df)
}
```

@@

@@

## Significance test for the percent presence of acquired genes between animal species
Only significant values will be presented in the table below (p < 0.05).
```{r message=FALSE, warning=FALSE}
acquired_genes_list <- resfinder_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, gene_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

p_values_acquired <- lapply(acquired_genes_list, function(x) do_chisq_test(x)) %>%
  bind_rows()

p_values_acquired
```

## Significance test for the percent presence of mutations in intrinsic genes between animal species
Only significant values will be presented in the table below (p < 0.05).

```{r message=FALSE, warning=FALSE}
mut_genes_list <- megares_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, mut_names) %>%
  filter(key != "acrB") %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

p_values_mut <-  lapply(mut_genes_list, function(x) do_chisq_test(x)) %>%
  bind_rows()

p_values_mut
```
